Accurate binding of sodium and calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-11-17 Manuscript/manuscript.tex
Few things I noticed during scanning the paper.

\subsection{Validation ECC-POPC model using binding affinities to Na$^+$ and Ca$^{2+}$ cations: the electrometer concept}

@@

\begin{table}[tb!]
  \caption{Bulk concentrations of Ca$^{2+}$ (C$_b$), relative surface excess of calcium with respect to water ($\Gamma_{Ca}^{\rm water}$),
    and the percetages of Ca$^{2+}$ bound to phosphate or carbonyl oxyges ($r^\mathrm{Ca^{2+}} _\mathrm{PO_4} $ and $r^\mathrm{Ca^{2+}} _\mathrm{O_{carb.}}$)
    in different POPC bilayer models. All systems have the same molar concentration of Ca$^{2+}$ respect to water ($C_{ion}'$=350mM).
    %{\color{red}HECTOR:PLEASE CHECK}
    %{\color{red}Joe, please confirm that $r^\mathrm{Ca^{2+}} _\mathrm{PO_4}$ is really 100\% for all the Lipid14 simulations
    %  (i.e. that this is not a typo).}
  \label{tab:binding}}
  \begin{tabular}{l|c c | c | c c}
    model                  & $C_{ion}'$ & $C_{ion}\,/\,\mathrm{mM}$ & $\Gamma_{Ca}^{\rm water} \,/\, \mathrm{nm}^{-2}$  & $r^\mathrm{Ca^{2+}} _\mathrm{PO_4} $ & $r^\mathrm{Ca^{2+}} _\mathrm{O_{carb.}} $ \\
    \hline
    ECC-POPC             &  350  &  $280\pm 10 $  &  $0.06 \pm 0.01 $                           &  99\%  &    25\%    \\
    Lipid14/\AA{}qvist     &  350  &  $210\pm 10 $  &  $0.13 \pm 0.01 $                          & 100\%  &    37\%     \\
    Lipid14/Dang           &  350  &  $160\pm 10 $  &  $0.23 \pm 0.03 $                            & 100\%  &    14\%    \\
    Lipid14/ECC-ions       &  350  &  $120\pm 100$  &  $0.35 \pm 0.11 $                         & 100\%  &    23\%    \\
%Average no. of bound cations:
%L14+Aqvist: all:22.7, phos:22.7, carb:8.5
%L14+Dang:   all:29.2, phos:29.2, carb:4.0
%L14+ECC-ion:all:37.7, phos:37.7, carb:8.5
  \end{tabular}
\end{table}

@@

\subsection{Binding stoichiometry of \ce{Na+} and \ce{Ca^{2+}} cations to the POPC membrane}

>>>>

\subsection{Validation of ECC-POPC model using binding affinities to Na$^+$ and Ca$^{2+}$ cations: the electrometer concept}

@@

\begin{table}[tb!]
  \caption{Bulk concentrations of Ca$^{2+}$ (C$_b$), relative surface excess of calcium with respect to water ($\Gamma_{Ca}^{\rm water}$),
    and the percetages of Ca$^{2+}$ bound to phosphate or carbonyl oxyges ($r^\mathrm{Ca^{2+}} _\mathrm{PO_4} $ and $r^\mathrm{Ca^{2+}} _\mathrm{O_{carb.}}$)
    in different POPC bilayer models. All systems have the same molar concentration of Ca$^{2+}$ with respect to water ($C_{ion}'$=350mM).
    %{\color{red}HECTOR:PLEASE CHECK}
    %{\color{red}Joe, please confirm that $r^\mathrm{Ca^{2+}} _\mathrm{PO_4}$ is really 100\% for all the Lipid14 simulations
    %  (i.e. that this is not a typo).}
  \label{tab:binding}}
  \begin{tabular}{l|c c | c | c c}
    model                  & $C_{ion}'$ & $C_{ion}\,/\,\mathrm{mM}$ & $\Gamma_{Ca}^{\rm water} \,/\, \mathrm{nm}^{-2}$  & $r^\mathrm{Ca^{2+}} _\mathrm{PO_4} $ & $r^\mathrm{Ca^{2+}} _\mathrm{O_{carb.}} $ \\
    \hline
    ECC-POPC             &  350  &  $280\pm 10 $  &  $0.06 \pm 0.01 $                           &  99\%  &    25\%    \\
    Lipid14/\AA{}qvist     &  350  &  $210\pm 10 $  &  $0.13 \pm 0.01 $                          & 100\%  &    37\%     \\
    Lipid14/Dang           &  350  &  $160\pm 10 $  &  $0.23 \pm 0.03 $                            & 100\%  &    14\%    \\
    Lipid14/ECC-ions       &  350  &  $120\pm 100$  &  $0.35 \pm 0.11 $                         & 100\%  &    23\%    \\
%Average no. of bound cations:
%L14+Aqvist: all:22.7, phos:22.7, carb:8.5
%L14+Dang:   all:29.2, phos:29.2, carb:4.0
%L14+ECC-ion:all:37.7, phos:37.7, carb:8.5
  \end{tabular}
\end{table}

@@

\subsection{Binding stoichiometry of \ce{Na+} and \ce{Ca^{2+}} cations to POPC membrane}
